Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2018-10-17 man/ms.Rmd
add more review

### Disturbance analyses 
Disturbance chronologies were built using tree-ring width to identify abrupt and sustained increases (release events from competition) or decreases (supressions) in radial growth [@Nowacki1997] as indirect estimates of possible disturbance events (e.g. logging) in the past. By using a temporal window of reasonable length this method is intended to filter out the response to short-term changes in temperature and precipitation and minimizes the long-term growth trends [@Nowacki1997; @Fraver2005].

@@

The trees of the southern population were older than northern ones, particularly for the high elevation site (CA-High) which had bigger and taller trees than the other sites (Tables 1, 2). `REVIEW meter en Discussion` This can be likely explained as a consequence of their different management origin (*i.e.* land-use legacy), as shown by the release event in SJ suggesting their coppice origin and (references). `END REVIEW` Competition was similar among sites but plot basal area was greatest in CA-High (Table 1), which however also exhibited the highest individual BAI growth (Figure 4). In addition, trees from this location showed a positive growth trend since the late 1970s (Figure 4), which was not found for any of the other two locations. For southern population differences in growth were observed, with CA-Low site showing lower values than CA-High but similar to growth values of the northern population (SJ) (Figure 4; Appendix S7).

@@

@@

The exploration of resilience metrics of tree-growth for other severe droughts, revealed a positive relation between resilience (*Rs*) and drought severity ($r^2$ = 0.336) (Appendix S5). A similar pattern was found for recovery (*Rc*; $r^2$ = 0.438) but negative for resistance (*Rt*, $r^2$ = 0.155). Resilience values of tree-growth for 2005 was the lowest of the drought events analyzed (Appendix S5) even not being the most severe drought events.

@@

## Forest disturbances
The analysis of growth changes revealed differences in forest history between sites (Figures 7 and 8). Northern site (SJ) showed two release events ($GC$ > 50 %) detected at stand-wise scale (occurring in more than 50 % of sampled trees): the first during the 1940 decade and the second in the period 1994-2001. These periods alternate with periods of supression. Southern sites (CA-High and CA-Low) showed some weak suppression episodes, but not in the last 50 years.

>>>>

### Disturbance analyses 
Disturbance chronologies were built using tree-ring width to identify abrupt and sustained increases (release events from competition) or decreases (supressions) in radial growth [@Nowacki1997] as indirect estimates of possible disturbance events (e.g. logging, neighbor mortality) in the past. By using a temporal window of reasonable length this method is intended to filter out the response to short-term changes in temperature and precipitation and minimizes the long-term growth trends [@Nowacki1997; @Fraver2005].

@@

The trees of the southern population were older than northern ones, particularly for the high elevation site (CA-High) which had bigger and taller trees than the other sites (Tables 1, 2). `REVIEW meter en Discussion` This can be likely explained as a consequence of their different management origin (*i.e.* land-use legacy), as shown by the release event in SJ suggesting their coppice origin and (references). `END REVIEW` Competition was similar among sites but plot basal area was greatest in CA-High (Table 1), which however also exhibited the highest individual BAI growth (Figure 4). `REVIEW` In addition, trees from this location showed a positive growth trend since the late 1970s (Figure 4), which was not found for any of the other two locations. `END REVIEW` For southern population differences in growth were observed. CA-Low growth was lower than that of CA-High but similar to growth of the northern population (SJ) (Figure 4; Appendix S7).

@@

The analysis of growth changes revealed differences in forest history between sites (Figures 7 and 8). Northern site (SJ) showed two release events ($GC$ > 50 %) detected at stand-wise scale (occurring in more than 50 % of sampled trees): the first during the 1940 decade and the second in the period 1994-2001. These periods alternate with periods of supression. Southern sites (CA-High and CA-Low) showed some weak suppression episodes, but not in the last 50 years.

The analysis of growth changes revealed differences in forest history between sites (Figures 7 and 8). Northern site (SJ) showed two release events (GC > 50 %) detected at stand-wise scale (occurring in more than 50 % of sampled trees): the first during the 1940 decade and the second in the period 1994-2001. These periods alternate with periods of supression. Southern sites (CA-High and CA-Low) showed no release event except one for CA-High at the beginning of the `REVIEW`1840s? and no suppression event in the last 50 years.

@@

The strength of the response of the resilience indices was related to drought severity. The exploration of resilience metrics of tree-growth for all severe droughts in our climatic data `REVIEW`(1900 - 2017), revealed a positive relation between resilience (*Rs*) and drought severity ($r^2$ = 0.336) (Appendix S5). A similar pattern was found for recovery (*Rc*; $r^2$ = 0.438) but negative for resistance (*Rt*, $r^2$ = 0.155). Resilience values of tree-growth for 2005 was the lowest of the drought events analyzed (Appendix S5) even not being the most severe drought events.

The exploration of resilience metrics of tree-growth for all severe droughts in our climatic data (period 1900-2017?),

@@
